---
title: "Primer Selection"
author: "Archarlie"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: FALSE
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(readr)
library(mosaic)
library(DT)
library(pander)
library(car)
library(ggplot2)
library(dplyr)
library(scales)
library(haven)
library(readxl)
library(downloader)
library(rio)
library(stringi)
library(viridis)
library(hrbrthemes)
library(ggridges)
library(lubridate)
library(riem)
library(hexbin)
library(RColorBrewer)
library(tidyquant)
library(quantmod)
library(dygraphs)
library(knitr)
library(tidyverse)
library(TmCalculator)
library(openPrimeR)
library(BiocManager)
library(plyr)
library(qpcR)
library(ggplot2)
library(stringi)
library(reticulate)
```

#  {.tabset .tabset-pills}


## Falnking (140)



### Original set of primers (130)

Gens mutation at the position are selected - "rs25", "rs16944", "rs1884", "rs17287498". Upstream sequence of 18 ~ 30 and the reverse primers are generated through primer3. 

```{r}

df <- read.csv("geenralprimerset.csv")[-c(1)]


DT::datatable(df)

```

## Mismacthing (72)



### Original set of mismatching primers (390)

A set of rules are applied to creat mismatches at the third position away from the gen mutation

```{r}

df <- read.csv("geenralprimerset.csv")
df <- df[c(2,3,4)]

####### creat mismatches functions

get_strong1 <- function(x){
  target <- str_sub(x , - 3, - 3) 
  target <- complement(target)
  
  if (target == "A") {temp <- "G"} else
    if (target == "G") {temp <- "A"} else
      if (target == "C") {temp <- "T"} else
        if (target == "T") {temp <- "C"}
  substring(x, nchar(x) - 2, nchar(x) - 2) <- temp
  return(x)
}

## Mismatching on Ts
get_strong2 <- function(x){
  target <- str_sub(x , - 3, - 3) 
  target <- complement(target)
  
  if (target == "T") {
    temp <- "T"
    substring(x, nchar(x) - 2, nchar(x) - 2) <- temp
    return(x)}
  else
    return(NULL)
}


get_medium1 <- function(x){
  target <- str_sub(x , - 3, - 3) 
  target <- complement(target)
  
  if (target == "A") {temp <- "A"} else
    if (target == "G") {temp <- "G"} else
      if (target == "C") {temp <- "C"} else
        return(NULL)
  
  substring(x, nchar(x) - 2, nchar(x) - 2) <- temp
  return(x)
}

get_weak1 <- function(x){
  target <- str_sub(x , - 3, - 3) 
  target <- complement(target)
  
  if (target == "C") {temp <- "A"} else
    if (target == "A") {temp <- "C"} else
      if (target == "G") {temp <- "T"} else
        if (target == "T") {temp <- "G"}
  substring(x, nchar(x) - 2, nchar(x) - 2) <- temp
  return(x)
}

# populate all the possible primers
mismatch_list <- df %>% 
  mutate(strong_mismatch_1 = map(forward, get_strong1),
         strong_mismatch_2 = map(forward, get_strong2),
         Medium_mismatch = map(forward, get_medium1),
         Weak_mismatch = map(forward, get_weak1))


Primer3_output <- mismatch_list[c(1,4,5,6,7,3)]

title <- rbind(cbind(paste(Primer3_output$name, "-","strong_mismatch_1")),
               cbind(paste(Primer3_output$name, "-","strong_mismatch_2")),
               cbind(paste(Primer3_output$name, "-","Medium_mismatch")),
               cbind(paste(Primer3_output$name, "-","Weak_mismatch")))


primers <- rbind(cbind(Primer3_output$strong_mismatch_1),
                 cbind(Primer3_output$strong_mismatch_2),
                 cbind(Primer3_output$Medium_mismatch),
                 cbind(Primer3_output$Weak_mismatch))

reverse <- rbind(cbind(mismatch_list$reverse),
                 cbind(mismatch_list$reverse),
                 cbind(mismatch_list$reverse),
                 cbind(mismatch_list$reverse))

Primer3_output <- cbind(title, primers, reverse)
colnames(Primer3_output) <- c("name", "forward", "reverse")
Primer3_output <- as.data.frame(Primer3_output) %>% 
  drop_na()


```


```{r}
## Make revers compliment

outputframe <- cbind(Primer3_output, "", "", "")

colnames(outputframe) <- c("name", "forward", "reverse", "revcom", "template", "name2")

reverse_chars <- function(string)
{
  # split string by characters
  string_split = strsplit(string, split = "")
  # reverse order
  rev_order = nchar(string):1
  # reversed characters
  reversed_chars = string_split[[1]][rev_order]
  # collapse reversed characters
  paste(reversed_chars, collapse = "")
} 

dymmy <- "AGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAGCTAG"


# Put name, template, reverse of complementary of reverse together
for (i in 1:nrow(outputframe)){
  outputframe[i,4] <- complement(unlist(outputframe[i,3]))
  outputframe[i,4] <- reverse_chars(unlist(outputframe[i,4]))
  outputframe[i,5] <- gsub(" ", "", paste(unlist(outputframe[i,2]), dymmy,
                                          unlist(outputframe[i,4]), sep = ""))
                           
}

outputframe <- outputframe[-c(6)]

#Enter output data frame into an input file for primer3
firstLine <- paste("SEQUENCE_ID=", outputframe$name, sep = "")
secondLine <- paste("SEQUENCE_TEMPLATE=", outputframe$template, sep = "")
thirdLine <- paste("SEQUENCE_PRIMER=", outputframe$forward, sep  = "")
fourthLine <- paste("SEQUENCE_PRIMER_REVCOMP=", outputframe$reverse, sep  = "")
otherLines <- "PRIMER_TASK=generic
PRIMER_OPT_SIZE=21
PRIMER_MIN_SIZE=15
PRIMER_MAX_SIZE=30
PRIMER_PRODUCT_SIZE_RANGE=30-500
PRIMER_EXPLAIN_FLAG=1
PRIMER_THERMODYNAMIC_OLIGO_ALIGNMENT=1
="

finalOutput <- paste(firstLine, secondLine, thirdLine, fourthLine, otherLines, sep = "\n")

write(finalOutput, "input0311_2.txt")

```


```{r message=FALSE, warning=FALSE}
primers <- read.delim("output311_2.txt", sep= '=', header = FALSE)


mismatch_filtered <- cbind(primers$V2[primers$V1 == "SEQUENCE_ID"], 
                  primers$V2[primers$V1 == "SEQUENCE_PRIMER"],
                  primers$V2[primers$V1 == "PRIMER_LEFT_0_HAIRPIN_TH"],
                  primers$V2[primers$V1 == "PRIMER_LEFT_0_END_STABILITY"],
                  primers$V2[primers$V1 == "PRIMER_RIGHT_0_END_STABILITY"],
                  primers$V2[primers$V1 == "PRIMER_LEFT_0_TM"],
                  primers$V2[primers$V1 == "PRIMER_RIGHT_0_TM"])

colnames(mismatch_filtered) <- c("ID", 
                        "LEFT_PRIMER", 
                        "HAIRPIN", 
                        "LEFT_STABILITY", 
                        "RIGHT_STABILITY", 
                        "LEFT_TM",
                        "RIGHT_TM")

mismatch_filtered <- as.data.frame(mismatch_filtered)

DT::datatable(mismatch_filtered)
```

### Mismatching primers with Filtering (72)

The filtering used are 1) TM_diff < 3 2) hairpin_stability = 0 3) both primers stability > 4.

```{r}
mismatch_filtered_real <- mismatch_filtered %>% 
  mutate(TM_diff = abs(as.numeric(LEFT_TM) - as.numeric(RIGHT_TM))) %>%
  filter(TM_diff < 3) %>%
  filter(as.numeric(HAIRPIN) < 12 &
           as.numeric(LEFT_STABILITY) > 3 &
           as.numeric(RIGHT_STABILITY) > 3) 


mismatch_filtered_real <- mismatch_filtered_real[-c(3,6,7)]

DT::datatable(mismatch_filtered_real)

```


## selection

asdasd



## Code





```{r}


```